### 2016-04-01 document/manuscript-plos.tex
move acknowledgements in manusctipt-plos.tex file, document funding sources

>>>>

\section*{Acknowledgments}

The authors would like to thank C. Titus Brown, Chris Fields and an
anonymous reviewer for their helpful comments in improving the
manuscript. We would also like to thank C. Titus Brown from
advertising contributions to the manuscript on social media, leading
to further contributions and improvements. We also thank Peter Cock
(peterjc) and and Kai Blin (kblin) for helpful suggestion contributed
directly though GitHub.
